\chapter{Conclusion and Outlook}
\label{chap:conclusion}


After experimenting with concepts made known in chapter \ref{chap:method}, reviewing the results and interpreting them, it is 
fitting to conclude this work. This chapter focuses firstly on what to take away and secondly on 
possible ablation studies or new concepts that could be researched based on this paper.


\section{Conclusion}
\label{sec:realconclusion}

\subsection{IAD Approaches on MVTecAD LOCO}
The survey on logical anomaly detection and localization using recent state-of-the-art IAD approaches went as expected. There was a performance drop that could at least 
partially be traced back to adding logical anomalies to the experiments. Moreover, the classifiers all exhibited reasonable sPRO metrics that were predictable for the 
other metrics. The results and discussion sections confirm that these approaches have a clear need for improvement when shifting the focus from the classic MVTecAD \cite{MVTEC_Bergmann_2021} 
to a more challenging dataset containing logical anomalies. This underlines one of the problems mentioned in the introduction: poor robustness for more complex anomalies. \newline
Judging from the segmentation results, these approaches have the potential to be adjusted for better logical anomaly localization performance. This could be done through 
further research for improved approaches or combining approaches to utilize different strengths. Examples of this are presented in the outlook.

\subsection{Flat Connector Class}
The novel dataset category is viable and allows further insights into various IAD methods. Its difficulty compared to other logical anomaly classes may be 
below average. However, this does not disqualify it from being a viable dataset extension. Having classes from multiple difficulties in one set helps evaluate classifiers on 
multiple levels and gives the opportunity for performance evaluation to strong and weaker approaches of IAD. Lastly, it extends the previously existing logical anomaly 
concepts, providing a more diverse experiment setting. \newline
The class may benefit from being extended regarding kinds of anomalies and more training and testing images. Ideas on potentially expanding this class are given 
in the outlook section of this chapter.

\subsection{Ensemble}
The ensemble approach presented in the previous chapters did not yield an improvement in robustness or any improvement in performance at all. The segmentations were either 
worse than the baseline or showed no learning process. The feature ensembling approach by Heller et al. \cite{EnsembleHeller2023} did not work in this setting. Applying it did not show any learning 
process (Fig. \ref{fig:pca_res}), and possible reasons were discussed in section \ref{subsec:ITBfaildiscussion}. This calls for further experimentation with this approach, as mentioned 
in the outlook. Stacking the channels to create merged feature maps did produce results that displayed potential. Still, the base ensemble methods had a better localization 
performance. On this basis, it is clear that merely feature map stacking is not a promising procedure for this problem statement. It should only be used  
with other methods to reduce and combine the number of channels.

\subsection{Current State of the Pipeline}
After the experiments are conducted, a code structure remains to be used for further experiments. 
All approaches discussed in this work are contained within the structure, and their functionality is adapted to experiment on the MVTecAD LOCO \cite{LOCODentsAndScratchesBergmann2022} dataset. Most 
importantly, an ensembling pipeline that allows ensemble members and ensembling methods to be switched modularly also exists. The ensembling members and methods 
serve as a two-part black box, both of which are likely root causes of failing ensemble performances. 
Through exchanging components in these regions, ablation studies can easily be performed on this topic, and the goal of achieving greater anomaly localization robustness 
could be realized with a different approach.


\section{Outlook}
\label{sec:finaloutlook}

After concluding the findings of this work, it is imperative to analyze aspects that could have been done differently or discuss new possible research that could emerge from 
the basis of this work and related work.\newline

\subsection{Current IAD Methods}
The conclusions drawn from the survey were reported in the previous section. The decreasing performance trend for logical anomaly detection in overall performance suggests 
current IAD approaches to be unsuitable for reaching the same effectiveness as on structural ones. This calls for a shift in the fundamental perspective of visual anomaly 
detection methods, tailoring them towards logical anomaly detection as in \cite{LOCODentsAndScratchesBergmann2022}, or trying to improve them by combining them to raise their 
performance. Solutions to this problem could combine 
those state-of-the-art methods into potentially more effective ones by using the upsides of multiple IAD methods to produce new approaches. An example would be a 
merger of the PatchCore \cite{patchCore2022} and SimpleNet \cite{liu2023simplenet} methods. Using a feature adapter trained in the latter approach to project feature 
representations before adding them to a memory bank is a promising step in this direction. 

\subsection{Novel Dataset Classes}
\label{subsec:FCoutlook}
Regarding the novel dataset category introduced in chapter \ref{chap:datasets}, it was apparent that the performance of all approaches was significantly higher than for other classes. 
As this may indicate that the class will be too easy, it is vital to look forward to either modifying the class or introducing new ones with similar representation in a 
manufacturing context. \newline
Concerning currently implemented logical anomalies of the flat connector class, it may be resource-extensive but worth producing anomalous flat connectors professionally. This 
could cause more real-looking anomalies and even help create new ones. For example, one could shift the position of a hole to a new logical anomaly category. Alternatively, the classes 
of missing holes could be produced free of artefacts, potentially leading to new results and more precise conclusions. Another way to extend the anomalies introduced for this 
object would be to work with arbitrary logical rules for collections of flat connectors. This could include presenting a grid of flat connectors and detecting missing or falsely 
oriented ones, similar to the pushpin class of the MVTecAD LOCO \cite{LOCODentsAndScratchesBergmann2022} dataset.\newline 
Since the effort to extend the logical anomaly dataset is ongoing, there are numerous possibilities on how to do so. Instances may include a class consisting of a metal angle. 
Constructing this class as a multiperspective dataset would be a noteworthy opportunity, as the angle may have different orientations and ambiguous positions. Depending 
on the orientation of the angle on the surface, one camera might not be able to capture every aspect of the three-dimensional object. An approach could be to learn several models 
from different perspectives and ensemble classifier outputs or even feature representations afterwards.

\subsection{Ensemble}
\label{subsec:ensembleconc}

\textbf{Backbones.} An outlook on backbones used for this work's ensemble approach is to conduct more experiments with either other backbones or a wider variety of hierarchies. 
This may be conducted in the same way as here or with potentially different architectures.
\newline\newline
\textbf{Ensembling Method.} The discussion made it apparent that the independent transformation block \cite{EnsembleHeller2023} or at least PCA is not applicable in this context. 
Still, there may be solutions to combine different feature representations more efficiently. In the case that the PCA did not work as intended on the features due to non-linear 
relationships of the variables, there are methods to overcome that problem. They include methods like t-SNE\cite{tSNE} or kernel PCA \cite{Hoffmann_2007kernelPCA}, both potentially 
viable methods for this problem. Furthermore, possibilities outside standard dimensionality reduction may be a base for new experiments. Possible approaches may include 
utilizing networks similar to the feature adapter approach from Simplenet (section \ref{subsec:simplenet}) to ensemble features channel-wise.
\newline\newline
\textbf{Feature Representations.} Lastly, as mentioned in the conclusion, the current ensemble network is currently a pipeline that consists of two black boxes, one for the ensemble 
members' feature representations and one for the chosen ensemble methods. The latter is covered in the last subsection. For the box of feature representations, ablation experiments are to be done using different IAD approaches. One could introduce new appropriate feature representations from different IAD methods to input to the ensemble pipeline for 
further studies.



\input{meta/acknowledgements.tex}


